Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-06 writeup/gz_hubble_data.tex
Sankey diagrams of sample

>>>>

\begin{figure*}
\center
\includegraphics[width=0.90\textwidth]{figures/sankey_both.png}
\caption{Demographics of the galaxy morphologies in GZH. Each node in each diagram (dark blue horizontal bars of uniform height) represents a task in the tree. The left diagram shows the full decision tree; the right diagram zooms in on the features/clumpy tasks, which are otherwise difficult to see. The paths between tasks represent each possible answer to the task; these flow from top to bottom between their origin question and the subsequent task in the tree. Labels are assigned to each galaxy based on the plurality answer for each task. A galaxy is assigned only one label at each node. Widths of the paths are proportional to the number of galaxies assigned to that path; the widths of the nodes are proportional to the number of galaxies for which the question was reliably answered.}
\label{fig:sankey}
\end{figure*}
